Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-12-16 bbbq_article.tex
Add sampling

The human immune system is unexpectedly attentive towards
human transmembrane helices (TMHs), as TMH-derived peptide fragments
bind to histocompatibility complex (MHC) class I more often then expected
by chance only, which can be mostly explained by the low hydrophobicity
of those residues.
The physiological reason is yet unclear,
yet this finding hints that there has been selection upon detecting TMH-derived
peptides in pathogens.
If this signature of selection is present in MHC-II is unknown.
This study shows that MHC-I [also has/does not have] more
epitopes derived from a TMH for a pathogen proteome, when compared with
a host proteome.
Additionally, MHC-II binds to peptides derived from TMHs 
more often than expected by chance.
Lastly, we show the TMHs are evolutionarily more conserved,
as less SNPs are found in TMH than expected by chance.
Our findings suggest that the immune system is more
vigilant to TMHs than expected by chance
and suggests that an evolutionary signal in the evolutionary history of a pathogen
may be found.

@@

{\bf Keywords:} antigen presentation, membrane proteins, bioinformatics, 
adaptive immunity, transmembrane domain, transmembrane helix, 
epitopes, T lymphocyte, MHC-I, MHC-II, SARS-CoV-2

@@

Regarding the evolutionary conservation of TMHs using SNPs,
again, it is estimated that approx 8.32 percent
of SNPs is caused, due to sequence variations in
highly similar duplicated sequences \cite{musumeci2010single}.
We assume that these duplications occur as often in TMHs as in
regions around these, hence we expect this not to affect our results.

>>>>

The human immune system is unexpectedly attentive towards
human transmembrane helices (TMHs), as TMH-derived peptide fragments
bind to histocompatibility complex (MHC) class I more often then expected
by chance only, which can be mostly explained by the low hydrophobicity
of those residues.
The physiological reason is yet unclear,
yet this finding hints that there has been selection upon detecting TMH-derived
peptides in pathogens.
If this signature of selection is present in MHC-II is unknown.
This study shows that MHC-I also has more
epitopes derived from a TMH for a pathogen proteome, when compared with
a host proteome.
Additionally, MHC-II binds to peptides derived from TMHs 
more often than expected by chance.
Lastly, we show the TMHs are evolutionarily more conserved,
as less SNPs are found in TMH than expected by chance.
Our findings suggest that the immune system is more
vigilant to TMHs than expected by chance
and suggests that an evolutionary signal in the evolutionary history of a pathogen
may be found.

@@

{\bf Keywords:} antigen presentation, membrane proteins, bioinformatics, 
adaptive immunity, transmembrane domain, transmembrane helix, 
epitopes, T lymphocyte, MHC-I, MHC-II, SARS-CoV-2, evolutionary conservation

@@

Regarding the evolutionary conservation of TMHs using SNPs,
again, it is estimated that approximately ten percent
of SNPs is a false positive that result from the methods to determine
a SNP. One example is that sequence variations are incorrectly
detected due to highly similar duplicated sequences \cite{musumeci2010single}.
We assume that these duplications occur as often in TMHs as in
regions around these, hence we expect this not to affect our results.

We used a low number of SNPs, as was imposed by the
NCBI API, which constrains its users to three calls per second.
As a second factor, we limited the time querying the NCBI database
for the duration of the project.
The SNPs we did use, we picked those
with the lowest SNP ID (which denotes the earliest discovery date) first.
We expect this not to introduce a bias, so we expect that
the SNPs we used are a representative sample of all SNPs.
